\documentclass[12pt]{article}
\usepackage{enumitem}
\title{Recape what you have learnt so far}
\author{SWATI SRI THINGBAIJAM}
\date{23th, September 2021}

\begin{document}
\maketitle
\pagenumbering{roman}
\section{First section}\label{sec1} 
The complex command of the list will provided in section.2
\\1. List the name of the fruits
\begin{itemize}
\item apple
\item mango
\end{itemize}
\begin{itemize}
\centering
\huge
\itshape
\item[wild animal $\diamond$] list the name of some animals
\item[$-$]tiger
\item[$-$]lion
\end{itemize}
\begin{itemize}
\item[$-$]second one
\item[$\ast$]third 
\item[$\diamond$]fourth
\end{itemize}
\begin{itemize}
\item[$=>$]Fifth 
\item[345].six.
\end{itemize}
\newpage
\section{Second section}\label{sec2}
In section 1, some fruits are listed. In this section, we will learn some advanced commands of list.
%\ref{sec3}
\begin{enumerate}[label={(\alph*)}]
\item one item 
\item[$****$]Printing of four stars. 
\item[$\#\#\#$]Printing of three hash.
\begin{enumerate}[label={(\alph*)}]
\item two item
\begin{enumerate}[label={(\arabic*)}]
\item third item 
\item [$\&\&\&$]Printing of three ampersands.
\item fourth item
\begin{enumerate}[label={(\roman*)}]
\item fifth item 
\item[$--- >$]Printing of arrow.
\item sixth item.
%\renewcommand{\labelitemiii}{\Alph{enumiv}}
\begin{enumerate}[label={\Alph*}]
\setcounter{enumiv}{3}
\item seventh item.
\item eighth item
\end{enumerate}
\end{enumerate}
\end{enumerate}
\item[$****$]Printing four stars.
\end{enumerate}
\end{enumerate}
\newpage
\section{Third section}\label{3}
\begin{itemize}
\item[$\ast$]this is the first point
\item[$\ast$]printing the asterik
\end{itemize}
\begin{itemize}
\item[.]this is the second point
\item[.]printing of dot
\end{itemize}
\begin{itemize}
\item[$\diamond$]this is the third point
\item[$\diamond$]printing of diamond
\end{itemize}
4th section starts
\begin{enumerate}[label={\arabic*}]
\item first item
\item first number of item
\begin{enumerate}[label={(\alph*)}]
\item second item
\item second number item
\begin{enumerate}[label={\roman*}]
\setcounter{enumiii}{4.}
\item third item
\item third number item
\begin{enumerate}[label={\Alph*}]
\setcounter{enumiv}{9.}
\item eight item
\item nine item
\end{enumerate}
\end{enumerate}
\end{enumerate}
\end{enumerate}
\end{enumerate}
\end{document}